---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MetadataApp

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of MetadataApp is to enable better content management. The app let's users create a batch file that will record metadata. After running the file, users can upload the results to get a tabular csv and visualise the output using the built-in functionalities of the app.

## Installation

The metadata app is currently not available for download.

``` r
install.packages("MetadataApp")
```

## Example

Example for this app will be provided upon request from the author.

```{r example, echo=FALSE}
library(MetadataApp)
## basic example code
```

Currently the only place to access this app is on shinyapps.io

https://client.shinyapps.io/MetadataApp_zhVqFYg6LV947ZFEJfHTpyKdQQ